Insect venom anaphylaxis: a case - control study of the European Anaphylaxis Registry

### 2019-05-13 analysis/paper/paper.Rmd
po konferencji w Groningen

## Managment
```{r}
testInsectsbinomialTab$management[,-7] %>% knitr::kable()
testInsectsbinomialTab$management[,-7]%>%
  tidyr::gather(value ="Proportion",
         key="Group",
         4:5) %>% 
  ggplot(aes(reorder(variableName,-Proportion),Proportion,fill=Group))+
  geom_bar(stat="identity",position="dodge")+
  theme(axis.text.x=element_text(angle=90))+
  geom_text(aes(y=0.5,label=reorder(signif(pval,2),-Proportion)),angle=90)
```

>>>>

## Managment
```{r}
testInsectsbinomialTab$management[,-7] %>% knitr::kable()
testInsectsbinomialTab$management[,-7]%>%
  tidyr::gather(value ="Proportion",
         key="Group",
         4:5) %>% 
  filter(variableName %in% c("q_522_cortico_iv","q_522_antih_iv","q_522_adren_im",
                             "q_522_adren_iv","q_522_antih_oral","q_522_beta2_inhal")) %>% 
  mutate(variableName = car::recode(
    variableName,recodes = "'q_522_cortico_iv'='corticoids iv.';
    'q_522_antih_iv'='antihistamines iv.';
    'q_522_adren_im'='adrenaline im.';
    'q_522_adren_iv'='adrenaline iv.';
    'q_522_antih_oral'='antihistamines po.';
    'q_522_beta2_inhal'='beta-2 mimetics inh.'"),
    Group = car::recode(Group,"'fraq_1'='IVA';
                        'fraq_2'='non-IVA'")) %>% 
  ggplot(aes(reorder(variableName,-Proportion),Proportion,fill=Group))+
  geom_bar(stat="identity",position="dodge")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 30,hjust =1),
        legend.position = c(1,1),
        legend.justification = c(1,1))+
  labs(x = "Symptoms",y = "Proportion of cases",fill="")+
  scale_fill_manual(values = rev(c("#E5F5E0", "#74C476","#005A32")))
  #geom_text(aes(y=0.5,label=reorder(signif(pval,2),-Proportion)),angle=90)
```
